Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-18 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued I} Updating

\begin{example}\label{ex:regular-pair}For any positive integer~$n$,
there is an additive interval-valued function\nb$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
defined by
\begin{equation}\eqalign{ 
\mathscr{I}_{n} = \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\ 
\iota_{n}\left(x\right) = \cases{ 
\left[\frac{k}{n},\frac{k}{n}\right] & , if $x=\frac{k}{n}$ ;\\ 
\left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
} 
}\end{equation}
Notice that the usual $\left\{ \necess,\imposs,\unknown\right\} $
is $\mathscr{I}_{1}$. Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
is an additive interval-valued function.\end{example}

\begin{proof}~
\begin{itemize}
\item $\iota\left(0\right)=\left[0,0\right]$. 
\item $\iota\left(1\right)=\left[1,1\right]$. 
\item When $x=k/n$, we have $\iota\left(1-x\right)=\left[1-k/n,1-k/n\right]=\left[1,1\right]-\iota\left(x\right)$.\\
When $k/n<x<\left(k+1\right)/n$, we have $1-k/n>1-x>1-\left(k+1\right)/n$
so that 
\begin{equation}
\iota\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\left[\frac{k}{n},\frac{k+1}{n}\right]=\left[1,1\right]-\iota\left(x\right)\textrm{ .}
\end{equation}
\item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{1}+x_{2}\right)\subseteq\iota\left(x_{1}\right)+\iota\left(x_{2}\right)$,
and the rest can be done by the induction. 
\begin{itemize}
\item When $x_{1}=k_{1}/n$, we have 
\begin{equation}
\iota\left(x_{1}+x_{2}\right)=\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota\left(x_{2}\right)=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .}
\end{equation}
\item When $k_{1}/n<x_{1}<\left(k_{1}+1\right)/n$ and $k_{2}/n<x_{2}<\left(k_{2}+1\right)/n$,
we have 
\begin{equation}
\frac{k_{1}+k_{2}}{n}<x_{1}+x_{2}<\frac{k_{1}+k_{2}+2}{n}
\end{equation}
so that 
\begin{equation}\eqalign{ 
& \iota\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\ 
= &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota\left(x_{1}\right)+\iota\left(x_{2}\right)\textrm{ .} 
}\end{equation}
\end{itemize}
\end{itemize}
\end{proof}

>>>>

\begin{example}\label{ex:regular-pair}For any positive integer~$n$
and $\delta\in\left[0,1\right]$, there is an additive interval-valued
function\nb$\iota_{n,\delta}:\left[0,1\right]\rightarrow\mathscr{I}_{n,\delta}$
defined by
\begin{equation}\eqalign{ 
\eqalign{\mathscr{I}_{n,\delta} =& \set{\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right]}{k=1,\ldots,n-1}\\
&\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\cup\left\{\left[0,0\right],\left[1,1\right]\right\}}\\ 
\iota_{n,\delta}\left(x\right) = \cases{ 
\left[x,x\right] & , if $x=0$ or  $x=1$ ;\\ 
\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right] & , if $x=\frac{k}{n}\in\left(0,1\right)$ ;\\ 
\left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
}
}\end{equation}
When we use the same notation in other place in this paper, we may
write $\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$ to represent
$\iota_{n,0}:\left[0,1\right]\rightarrow\mathscr{I}_{n,0}$. Notice
that the usual $\left\{ \necess,\imposs,\unknown\right\} $ is $\mathscr{I}_{1}$.
Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
is an additive interval-valued function.\end{example}

\begin{proof}~
\begin{itemize}
\item Since $\delta\in\left[0,1\right]$ and $\iota_{n,\delta}\left(x\right)=\left[\frac{k-\delta}{n},\frac{k+\delta}{n}\right]$
only when $0<x=\frac{k}{n}<1$, we have $\iota_{n,\delta}\left(x\right)\subseteq\left[0,1\right]$.
\item $\iota_{n,\delta}\left(0\right)=\left[0,0\right]$. 
\item $\iota_{n,\delta}\left(1\right)=\left[1,1\right]$. 
\item When $x=0$ or $x=1$, we have $\iota_{n,\delta}\left(1-x\right)=\left[1-x,1-x\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)$.\\
When $x=k/n\in\left(0,1\right)$, we have 
\begin{equation}
\iota_{n,\delta}\left(1-x\right)=\left[\frac{n-k-\delta}{n},\frac{n-k+\delta}{n}\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)\textrm{ .}
\end{equation}
When $k/n<x<\left(k+1\right)/n$, we have $1-k/n>1-x>1-\left(k+1\right)/n$
so that 
\begin{equation}
\iota_{n,\delta}\left(1-x\right)=\left[1-\frac{k+1}{n},1-\frac{k}{n}\right]=\left[1,1\right]-\iota_{n,\delta}\left(x\right)\textrm{ .}
\end{equation}
\item It is sufficient to prove the case when $N=2$, i.e., for a set $\left\{ x_{1},x_{2}\right\} \subseteq\left[0,1\right]$,
if $x_{1}+x_{2}\in\left[0,1\right]$, then $\iota_{n,\delta}\left(x_{1}+x_{2}\right)\subseteq\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)$,
and the rest can be done by the induction. 
\begin{itemize}
\item When $x_{1}=0$, we have $\iota_{n,\delta}\left(x_{1}+x_{2}\right)=\iota_{n,\delta}\left(x_{2}\right)=\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)$.
\item When $x_{1}=k_{1}/n\in\left(0,1\right)$, we have 
\begin{equation}
\iota_{n,\delta}\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota_{n,\delta}\left(x_{2}\right)\subseteq\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)\textrm{ ,}
\end{equation}
where $\iota_{n,\delta}\left(x_{1}+x_{2}\right)$ is a proper subset
of $\left[\frac{k_{1}}{n},\frac{k_{1}}{n}\right]+\iota_{n,\delta}\left(x_{2}\right)$
only when $x_{1}+x_{2}=1$.
\item When $k_{1}/n<x_{1}<\left(k_{1}+1\right)/n$ and $k_{2}/n<x_{2}<\left(k_{2}+1\right)/n$,
we have 
\begin{equation}
\frac{k_{1}+k_{2}}{n}<x_{1}+x_{2}<\frac{k_{1}+k_{2}+2}{n}
\end{equation}
so that 
\begin{equation}\eqalign{ 
& \iota_{n,\delta}\left(x_{1}+x_{2}\right)\subseteq\left[\frac{k_{1}+k_{2}}{n},\frac{k_{1}+k_{2}+2}{n}\right]\\ 
= &\left[\frac{k_{1}}{n},\frac{k_{1}+1}{n}\right]+\left[\frac{k_{2}}{n},\frac{k_{2}+1}{n}\right]=\iota_{n,\delta}\left(x_{1}\right)+\iota_{n,\delta}\left(x_{2}\right)\textrm{ .} 
}\end{equation}
\end{itemize}
\end{itemize}
\end{proof}
